Technology-based aids for people affected by Autism Spectrum Disorder (ASD)

### 2017-11-16 paper.tex
Finish part about first paper

The key point is that the information received on the screen of the therapist interface shows a real time image of the child and monitored progress statistics.
Since the VA that the child observes on his screen is a disguise of his therapist, combined with artificial intelligence, is actually the therapist who promotes the interaction in combination with the expert system.

>>>>

The choices about the best \gls{va} to use during the sessions, or the characteristics that has to be changed in the current \gls{va}, are taken monitoring the reaction of the child when he's put in front of them.
The character can be not strictly a human, since the highest degree of affinity can be towards an animal or an object.

The key point in their work is that the information received on the screen of the therapist interface shows a real time image of the child and monitored progress statistics.
Since the VA that the child observes on his screen is a disguise of his therapist, combined with artificial intelligence, is actually the therapist who promotes the interaction in combination with the expert system.

\subsection{A more complex system}
\label{sec:avatar_complex}

Another more complex and complete approach was performed in \cite{Alahbabi17}, using a robot instead of a \gls{va}, since it has been shown in \cite{Pioggia08} that patients show a more favorable response towards humanoid robots than to other non-humanoid virtual characters.

This approach has sensible advantages but also some intrinsic shortcomings:
\begin{itemize}
	\item most of the robotic or virtualized therapy are preprogrammed, that make the session boring and repetitive;
	\item robots are limited and work in a controlled environment;
	\item usually robots don't have a quantitative behavioral analysis tool due to the absence of therapists during their development process.
\end{itemize}
